Weighted Model Counting with Conditional Weights for Bayesian Networks

### 2021-05-22 doc/UAI_paper/paper.tex
Start working on the poster

\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
% TODO: maybe I should rotate the cumulative plot

% TODO: read 'Preparing the submission materials' (code: dilkas_167)
% TODO: update the abstract during submission

@@

% TODO: must reference the SAT paper and explain the differences
% \cite{my_sat_paper}

>>>>

\title{Weighted Model Counting with Conditional Weights for Bayesian Networks}
% TODO: maybe I should rotate the cumulative plot
% TODO: read 'Preparing the submission materials' (code: dilkas_167)
% TODO: update the abstract during submission

@@

While in this paper we focus on measure-theoretic foundations and propose a
new encoding for Bayesian networks, a related line of work
\citep{my_sat_paper}---motivated by the same issue of WMC encodings having both
more variables and more clauses as a consequence of having to conform to an
unnecessarily restrictive format---shows how these variables and clauses can be
removed from (most) already-existing Bayesian network encodings. Although tested
on Bayesian networks, this variable removal is formulated in a way that applies
to arbitrary WMC instances.
% I could also mention DPMC vs ADDMC and pseudo-Boolean functions
